---
title: "Data_exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data_exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HMM)
```

```{r}
library(HMM)
library(NLP)
```

Penn_Treebank_POS_tags
   entry                                  description
1      $                                       dollar
2     ``                       opening quotation mark
3     ''                       closing quotation mark
4      (                          opening parenthesis
5      )                          closing parenthesis
6      ,                                        comma
7      -                                         dash
8      .                          sentence terminator
9      :                            colon or ellipsis
10    CC                    conjunction, coordinating
11    CD                            numeral, cardinal
12    DT                                   determiner
13    EX                            existential there
14    FW                                 foreign word
15    IN    preposition or conjunction, subordinating
16    JJ                adjective or numeral, ordinal
17   JJR                       adjective, comparative
18   JJS                       adjective, superlative
19    LS                             list item marker
20    MD                              modal auxiliary
21    NN               noun, common, singular or mass
22   NNP                       noun, proper, singular
23  NNPS                         noun, proper, plural
24   NNS                         noun, common, plural
25   PDT                               pre-determiner
26   POS                              genitive marker
27   PRP                            pronoun, personal
28  PRP$                          pronoun, possessive
29    RB                                       adverb
30   RBR                          adverb, comparative
31   RBS                          adverb, superlative
32    RP                                     particle
33   SYM                                       symbol
34    TO     "to" as preposition or infinitive marker
35    UH                                 interjection
36    VB                              verb, base form
37   VBD                             verb, past tense
38   VBG           verb, present participle or gerund
39   VBN                        verb, past participle
40   VBP verb, present tense, not 3rd person singular
41   VBZ     verb, present tense, 3rd person singular
42   WDT                                WH-determiner
43    WP                                   WH-pronoun
44   WP$                       WH-pronoun, possessive
45   WRB                                    Wh-adverb


```{r}
POS = list(word = ,tag)
words <- sapply(POS, function(x) x$word)
tags <- sapply(POS, function(x) x$tag)

# Splitting the dataset into training and testing sets
set.seed(123) # for reproducible results
sample_size <- floor(0.8 * length(words))
train_indices <- sample(seq(length(words)), sample_size)
test_indices <- setdiff(seq(length(words)), train_indices)

train_words <- words[train_indices]
train_tags <- tags[train_indices]
test_words <- words[test_indices]
test_tags <- tags[test_indices]

```

